Manuscript Figures

### 2018-06-07 Manuscript Figures.Rmd
Average FPKMs by subgenome favors maize2 often

>>>>

```{r extra4, echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=4, fig.height=4, fig.align='center'}
# Average expression for genes in each subgenome, biased by sample size.  While other plots show that maize1 dominates maize2 more often in all tissue, maize2 
# for pollen and endosperm crown the average expression is higher in maize2.  Basically, when maize2 wins, it wins by more raw FPKMs.  If we account for all
# genes in the subgenome, not just the pairs, maize2 often has higher average expression.  This is probably due to many very low expressed genes in maize1.
data <- 
  homeologs.pairs %>%
  # subset(Maize1 != "" & Maize2 != "") %>%
  # select(Maize1, Maize2) %>%
  distinct() %>%
  select(Maize1, Maize2) %>%
  left_join(maize.walley.v4mapped.expression, by=c("Maize1"="geneID")) %>%
  rename(FPKM_avg1=FPKM_avg) %>%
  left_join(maize.walley.v4mapped.expression, by=c("Maize2"="geneID", "sample"="sample")) %>%
  rename(FPKM_avg2=FPKM_avg) %>%
  select(Maize1, Maize2, sample, FPKM_avg1, FPKM_avg2) %>%
  # subset(sample %in% c("B73 Mature Pollen")) %>%
  group_by(sample) %>%
  summarize(Mean1=mean(FPKM_avg1, na.rm=TRUE), Mean2=mean(FPKM_avg2, na.rm=TRUE))
data <- 
  data %>%
  gather(subgenome, FPKM, -1)

ggplot(data, aes(x=sample, y=FPKM, fill=subgenome)) + geom_col(position = position_dodge()) + theme(axis.text.x=element_text(angle=90,hjust=1))
```
